### 2025-08-07 data-analysis/outputs/first_stage_sibship.tex
add output tables for birthrate and DHS descriptive stats
Added LaTeX output files for census birthrate changes and various DHS descriptive and summary statistics tables. These outputs summarize birth rates by region and period, and provide detailed descriptive statistics for outcomes by location and policy period.

[1] "Non-NCR, Pre-Policy"  "Non-NCR, Post-Policy"
[1] "Non-NCR, Pre-Policy"  "Non-NCR, Post-Policy"

@@

[136] "datum"                         "manila"                        "treated"                      
[139] "birth_year_relative_to_policy" "post_policy"                   "urban"                        
[142] "mother_educ_years"             "number_of_siblings"            "ncr"                          
[145] "num_vaccines"                  "location_group"                "group"                        

@@

[136] "datum"                         "manila"                        "treated"                      
[139] "birth_year_relative_to_policy" "post_policy"                   "urban"                        
[142] "mother_educ_years"             "number_of_siblings"            "ncr"                          
[145] "num_vaccines"                  "location_group"                "group"                        
Ncells    3222493   172.1    5740976   306.7    5740976   306.7
Vcells 2622053306 20004.7 5428700101 41417.7 5975044060 45586.0
[1] 7
[1] 7
[1] 7

|Variable                 |123                  |136                  |151                  |209                  |3410                 |7437                 |
|:------------------------|:--------------------|:--------------------|:--------------------|:--------------------|:--------------------|:--------------------|
|Birth weight (grams)     |5816.11 \\ (3592.43) |5379.28 \\ (3411.51) |3937.93 \\ (2439.54) |4766.51 \\ (3089.10) |5254.08 \\ (3321.64) |5754.47 \\ (3399.87) |
|1 - Very small           |2 (1.6%)             |NA                   |1 (0.7%)             |10 (4.8%)            |116 (3.4%)           |345 (4.7%)           |
|2 - Smaller than average |25 (20.3%)           |34 (25.0%)           |38 (25.2%)           |35 (16.8%)           |584 (17.2%)          |1256 (17.0%)         |
|3 - Average size         |76 (61.8%)           |84 (61.8%)           |84 (55.6%)           |122 (58.7%)          |1990 (58.6%)         |4397 (59.4%)         |
|4 - Larger than average  |18 (14.6%)           |15 (11.0%)           |18 (11.9%)           |28 (13.5%)           |509 (15.0%)          |970 (13.1%)          |
|5 - Very large           |2 (1.6%)             |3 (2.2%)             |10 (6.6%)            |12 (5.8%)            |184 (5.4%)           |407 (5.5%)           |
|9 - Missing              |NA                   |NA                   |NA                   |1 (0.5%)             |NA                   |18 (0.2%)            |
|8 - Don’t know           |NA                   |NA                   |NA                   |NA                   |14 (0.4%)            |13 (0.2%)            |
|1–2 Vaccines             |1 (0.8%)             |3 (2.2%)             |3 (2.0%)             |1 (0.5%)             |95 (2.8%)            |68 (0.9%)            |
|3–4 Vaccines             |3 (2.4%)             |5 (3.7%)             |5 (3.3%)             |4 (1.9%)             |117 (3.4%)           |136 (1.8%)           |
|5+ Vaccines              |31 (25.2%)           |52 (38.2%)           |29 (19.2%)           |38 (18.2%)           |1141 (33.5%)         |1869 (25.1%)         |
|No Vaccines              |88 (71.5%)           |76 (55.9%)           |114 (75.5%)          |166 (79.4%)          |2057 (60.3%)         |5364 (72.1%)         |

|Variable                 |123                  |136                  |151                  |209                  |3410                 |7437                 |
|:------------------------|:--------------------|:--------------------|:--------------------|:--------------------|:--------------------|:--------------------|
|Birth weight (grams)     |5816.11 \\ (3592.43) |5379.28 \\ (3411.51) |3937.93 \\ (2439.54) |4766.51 \\ (3089.10) |5254.08 \\ (3321.64) |5754.47 \\ (3399.87) |
|1 - Very small           |2 (1.6%)             |NA                   |1 (0.7%)             |10 (4.8%)            |116 (3.4%)           |345 (4.7%)           |
|2 - Smaller than average |25 (20.3%)           |34 (25.0%)           |38 (25.2%)           |35 (16.8%)           |584 (17.2%)          |1256 (17.0%)         |
|3 - Average size         |76 (61.8%)           |84 (61.8%)           |84 (55.6%)           |122 (58.7%)          |1990 (58.6%)         |4397 (59.4%)         |
|4 - Larger than average  |18 (14.6%)           |15 (11.0%)           |18 (11.9%)           |28 (13.5%)           |509 (15.0%)          |970 (13.1%)          |
|5 - Very large           |2 (1.6%)             |3 (2.2%)             |10 (6.6%)            |12 (5.8%)            |184 (5.4%)           |407 (5.5%)           |
|9 - Missing              |NA                   |NA                   |NA                   |1 (0.5%)             |NA                   |18 (0.2%)            |
|8 - Don’t know           |NA                   |NA                   |NA                   |NA                   |14 (0.4%)            |13 (0.2%)            |
|1–2 Vaccines             |1 (0.8%)             |3 (2.2%)             |3 (2.0%)             |1 (0.5%)             |95 (2.8%)            |68 (0.9%)            |
|3–4 Vaccines             |3 (2.4%)             |5 (3.7%)             |5 (3.3%)             |4 (1.9%)             |117 (3.4%)           |136 (1.8%)           |
|5+ Vaccines              |31 (25.2%)           |52 (38.2%)           |29 (19.2%)           |38 (18.2%)           |1141 (33.5%)         |1869 (25.1%)         |
|No Vaccines              |88 (71.5%)           |76 (55.9%)           |114 (75.5%)          |166 (79.4%)          |2057 (60.3%)         |5364 (72.1%)         |
Ncells  3222541 172.2    5740976   306.7    5740976   306.7
Vcells 24136690 184.2 4342960081 33134.2 5975044060 45586.0
Ncells  3220838 172.1    5740976   306.7    5740976   306.7
Vcells 24001138 183.2 3474368065 26507.4 5975044060 45586.0
 [1] "\\begin{table}[H][!h]"                                          
 [2] "\\centering"                                                    
 [3] "\\caption{Average Birth Weight by Location and Policy Period}"  
 [4] "\\centering"                                                    
 [5] "\\begin{tabular}[t]{lc}"                                        
 [6] "\\toprule"                                                      
 [7] "Group & Birth weight (g)\\\\"                                   
 [8] "\\midrule"                                                      
 [9] "Manila, Pre-Policy & \\makecell{4766.51 \\\\ (3089.10)}\\\\"    
[10] "Manila, Post-Policy & \\makecell{3864.21 \\\\ (2419.37)}\\\\"   
[11] "Other NCR, Pre-Policy & \\makecell{5816.11 \\\\ (3592.43)}\\\\" 
[12] "Other NCR, Post-Policy & \\makecell{5379.28 \\\\ (3411.51)}\\\\"
[13] "Non-NCR, Pre-Policy & \\makecell{5754.47 \\\\ (3399.87)}\\\\"   
[14] "Non-NCR, Post-Policy & \\makecell{5254.08 \\\\ (3321.64)}\\\\"  
[15] "\\bottomrule"                                                   
[16] "\\end{tabular}"                                                 
[17] "\\end{table}"                                                   
 [1] "\\begin{table}[H][!h]"                                          
 [2] "\\centering"                                                    
 [3] "\\caption{Average Birth Weight by Location and Policy Period}"  
 [4] "\\centering"                                                    
 [5] "\\begin{tabular}[t]{lc}"                                        
 [6] "\\toprule"                                                      
 [7] "Group & Birth weight (g)\\\\"                                   
 [8] "\\midrule"                                                      
 [9] "Manila, Pre-Policy & \\makecell{4766.51 \\\\ (3089.10)}\\\\"    
[10] "Manila, Post-Policy & \\makecell{3864.21 \\\\ (2419.37)}\\\\"   
[11] "Other NCR, Pre-Policy & \\makecell{5816.11 \\\\ (3592.43)}\\\\" 
[12] "Other NCR, Post-Policy & \\makecell{5379.28 \\\\ (3411.51)}\\\\"
[13] "Non-NCR, Pre-Policy & \\makecell{5754.47 \\\\ (3399.87)}\\\\"   
[14] "Non-NCR, Post-Policy & \\makecell{5254.08 \\\\ (3321.64)}\\\\"  
[15] "\\bottomrule"                                                   
[16] "\\end{tabular}"                                                 
[17] "\\end{table}"                                                   
Ncells  3220342 172.0    5740976   306.7    5740976   306.7
Vcells 24001025 183.2 2779494452 21205.9 5975044060 45586.0
# A tibble: 6 × 136
  case_id           cluster_id household_id sample_weight mother_age_current residence_type household_size
  <chr>                  <dbl>        <dbl>         <dbl>              <dbl> <dbl+lbl>               <dbl>
1 "       1   2  2"          1            2       1452369                 27 1 [urban]                   3
2 "       1   3  2"          1            3       1452369                 23 1 [urban]                   4
3 "       1   3  2"          1            3       1452369                 23 1 [urban]                   4
4 "       1   4  2"          1            4       1452369                 21 1 [urban]                  11
5 "       1   4  2"          1            4       1452369                 21 1 [urban]                  11
6 "       1   4  9"          1            4       1452369                 24 1 [urban]                  11
# ℹ 129 more variables: household_u5_count <dbl>, region <dbl+lbl>, province <dbl+lbl>, municipality <dbl>,
#   wealth_index <dbl+lbl>, wealth_score <dbl>, birth_index <dbl>, birth_order <dbl>, is_twin <dbl+lbl>,
#   birth_month <dbl>, birth_year <dbl>, birth_date <dbl>, child_sex <dbl+lbl>, child_alive <dbl+lbl>,
#   age_at_death <dbl+lbl>, child_age <dbl>, preceding_birth_interval <dbl>, succeeding_birth_interval <dbl>,
#   delivery_place <dbl+lbl>, birth_size <dbl+lbl>, birth_weight <dbl+lbl>, received_bcg <dbl+lbl>,
#   bcg_day <dbl+lbl>, bcg_month <dbl+lbl>, bcg_year <dbl+lbl>, received_dpt1 <dbl+lbl>, dpt1_day <dbl+lbl>,
#   dpt1_month <dbl+lbl>, dpt1_year <dbl+lbl>, received_polio1 <dbl+lbl>, polio1_day <dbl+lbl>, …
# ℹ Use `colnames()` to see all variable names

@@

[136] "datum"                    

@@

[136] "datum"                    
[136] "datum"                    
Ncells  3366595 179.8    5740976   306.7    5740976   306.7
Vcells 24254013 185.1 2223595562 16964.7 5975044060 45586.0
[136] "datum"                    
[136] "datum"                    
[136] "datum"                    
[136] "datum"                    
[136] "datum"                    
[136] "datum"                    
[136] "datum"                    
[136] "datum"

>>>>

\begin{table}
\centering
\begin{talltblr}[         %% tabularray outer open
entry=none,label=none,
note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
note{ }={All regressions include survey year fixed effects.},
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]},
column{2,3}={}{halign=c,},
column{1}={}{halign=l,},
hline{10}={1,2,3}{solid, black, 0.05em},
}                     %% tabularray inner close
\toprule
& (1) & (2) \\ \midrule %% TinyTableHeader
Manila × Post & \num{0.231} & \num{0.100}+ \\
& (\num{0.227}) & (\num{0.077}) \\
Mother's Education & \num{-0.393}*** & \num{-0.315}*** \\
& (\num{<0.001}) & (\num{<0.001}) \\
Mother's Age & \num{0.230}** & \num{0.207}** \\
& (\num{0.003}) & (\num{0.001}) \\
Wealth Index & \num{-0.287}*** & \num{-0.247}** \\
& (\num{<0.001}) & (\num{0.002}) \\
Num.Obs. & \num{20823} & \num{20823} \\
R2 & \num{0.539} & \num{0.514} \\
R2 Adj. & \num{0.539} & \num{0.513} \\
R2 Within & \num{0.535} & \num{0.511} \\
R2 Within Adj. & \num{0.535} & \num{0.511} \\
RMSE & \num{1.65} & \num{1.53} \\
FE: survey_year & X & X \\
\bottomrule
\end{talltblr}
\end{table} 
\begin{table}
\centering
\begin{talltblr}[         %% tabularray outer open
entry=none,label=none,
note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
note{ }={All regressions include survey year fixed effects.},
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]},
column{2,3}={}{halign=c,},
column{1}={}{halign=l,},
hline{10}={1,2,3}{solid, black, 0.05em},
}                     %% tabularray inner close
\toprule
& (1) & (2) \\ \midrule %% TinyTableHeader
Manila × Post & \num{0.231} & \num{0.100}+ \\
& (\num{0.227}) & (\num{0.077}) \\
Mother's Education & \num{-0.393}*** & \num{-0.315}*** \\
& (\num{<0.001}) & (\num{<0.001}) \\
Mother's Age & \num{0.230}** & \num{0.207}** \\
& (\num{0.003}) & (\num{0.001}) \\
Wealth Index & \num{-0.287}*** & \num{-0.247}** \\
& (\num{<0.001}) & (\num{0.002}) \\
Num.Obs. & \num{20823} & \num{20823} \\
R2 & \num{0.539} & \num{0.514} \\
R2 Adj. & \num{0.539} & \num{0.513} \\
R2 Within & \num{0.535} & \num{0.511} \\
R2 Within Adj. & \num{0.535} & \num{0.511} \\
FE: survey\_year & X & X \\
\bottomrule
\end{talltblr}
\end{table} 
\begin{table}
\centering
\begin{talltblr}[         %% tabularray outer open
entry=none,label=none,
note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
note{ }={All regressions include survey year fixed effects.},
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]},
column{2,3}={}{halign=c,},
column{1}={}{halign=l,},
hline{10}={1,2,3}{solid, black, 0.05em},
}                     %% tabularray inner close
\toprule
& (1) & (2) \\ \midrule %% TinyTableHeader
Manila × Post & \num{0.100}+ & \num{0.231} \\
& (\num{0.077}) & (\num{0.227}) \\
Mother's Education & \num{-0.315}*** & \num{-0.393}*** \\
& (\num{<0.001}) & (\num{<0.001}) \\
Mother's Age & \num{0.207}** & \num{0.230}** \\
& (\num{0.001}) & (\num{0.003}) \\
Wealth Index & \num{-0.247}** & \num{-0.287}*** \\
& (\num{0.002}) & (\num{<0.001}) \\
Num.Obs. & \num{20823} & \num{20823} \\
R2 & \num{0.514} & \num{0.539} \\
R2 Adj. & \num{0.513} & \num{0.539} \\
R2 Within & \num{0.511} & \num{0.535} \\
R2 Within Adj. & \num{0.511} & \num{0.535} \\
FE: survey\_year & X & X \\
\bottomrule
\end{talltblr}
\end{table} 
\begin{table}
\centering
\begin{talltblr}[         %% tabularray outer open
entry=none,label=none,
note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
note{ }={All regressions include survey year fixed effects.},
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]},
column{2,3}={}{halign=c,},
column{1}={}{halign=l,},
hline{10}={1,2,3}{solid, black, 0.05em},
}                     %% tabularray inner close
\toprule
& (1) & (2) \\ \midrule %% TinyTableHeader
Manila × Post & \num{0.100}+ & \num{0.231} \\
& (\num{0.077}) & (\num{0.227}) \\
Mother's Education & \num{-0.315}*** & \num{-0.393}*** \\
& (\num{<0.001}) & (\num{<0.001}) \\
Mother's Age & \num{0.207}** & \num{0.230}** \\
& (\num{0.001}) & (\num{0.003}) \\
Wealth Index & \num{-0.247}** & \num{-0.287}*** \\
& (\num{0.002}) & (\num{<0.001}) \\
Num.Obs. & \num{20823} & \num{20823} \\
R2 & \num{0.514} & \num{0.539} \\
R2 Adj. & \num{0.513} & \num{0.539} \\
R2 Within & \num{0.511} & \num{0.535} \\
R2 Within Adj. & \num{0.511} & \num{0.535} \\
FE: survey\_year & X & X \\
\bottomrule
\end{talltblr}
\end{table} 
Ncells 2386672 127.5    3882202 207.4  3882202 207.4
Vcells 8326641  63.6   26574801 202.8 26574145 202.8

@@

[136] "datum"                     "number_of_siblings"        "manila"                   
[139] "post_policy"               "manila_post"              

@@

[136] "datum"                     "number_of_siblings"        "manila"                   
[139] "post_policy"               "manila_post"              

@@

[136] "datum"                     "number_of_siblings"        "manila"                   
[139] "post_policy"               "manila_post"              

@@

[136] "datum"                     "number_of_siblings"        "manila"                   
[139] "post_policy"               "manila_post"
